---
title: "Customizing Questions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customizing Questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r warning=FALSE, message=FALSE, include=FALSE}
pkgload::load_all()
```

`shinyQuiz` provides versatile functions customizing your questions beyond the predefined question types. By using `create_question()` and `create_question_raw()` functions, you can tailor your quizzes to suit a wide array of educational scenarios and learning styles.
In this guide, we will delve into the power of these two functions, demonstrating how to craft custom questions, specify multiple correct answers, and incorporate raw HTML for enhanced question formatting.

```{r setup}
library(shinyQuiz)
```

## Maximizing `create_question()`

`create_question()` can take a HTML in its prompt. 

...expand on plots, html, etc...

```{r eval=FALSE}
create_question(
  htmltools::div(
    htmltools::p("A custom question with a plot"),
    shiny::renderPlot(plot(rnorm(100), rnorm(100))),
  ),
  add_slider(10, 50, 30, correct = 20),
  label = 'Select 20'
)
```

## Further customization via `create_question_raw()`

### Customizing prompts

`create_question` can take html but `create_question_raw` is even more flexible.

```{r eval=FALSE}
create_question_raw()
```

<br>

## More Coming Soon!!

### Customizing inputs


<br>

### Customizing grading

