---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r warning=FALSE, message=FALSE, include=FALSE}
pkgload::load_all()
```


`shinyQuiz` is a powerful R package that allows users to create interactive quizzes within R Shiny applications. This guide provides a step-by-step introduction to creating a quiz, integrating it into your Shiny app, and adjusting the options.

## Installation

`shinyQuiz` is currently in development and is available to test by installing via:

<!-- TODO: update with CRAN when ready -->

``` r
# latest development version
# install.packages("remotes")
remotes::install_github('priism-center/shinyQuiz')
```


## Creating questions

To start creating a quiz, first load the package.


```{r setup}
library(shinyQuiz)
```

A quiz is composed of individual questions created via the `create_question` function. These objects are then integrated into a quiz using the `create_quiz` function.

Individual questions take a prompt and an arbitrary amount of answer choices via `add_numeric()`, `add_choice()`, or `add_slider()`,

```{r}
q1 <- create_question(
  'What is 2+2?',
  add_numeric(correct = 4)
)
```

```{r}
q2 <- create_question(
  'What is the capital of France?',
  add_choice('Lyon'),
  add_choice('Paris', correct = TRUE),
  add_choice('Strasbourg'),
  label = 'Select a city'
)
```

```{r}
q3 <- create_question(
  'Which cities are capital cities?',
  add_choice('Paris', correct = TRUE),
  add_choice('London', correct = TRUE),
  add_choice('Munich'),
  label = 'Select all that are correct'
)
```

```{r}
q4 <- create_question(
  'What is 1.5 / 2?',
  add_slider(correct = 0.75)
)
```

<br>

## Forming a quiz

Create the quiz and preview it.

```{r}
quiz <- create_quiz(q1, q2, q3, q4)
```

The `preview_app()` launches the quiz in a Shiny instance. This can be used directly if you wish.

```{r eval=FALSE}
preview_app(quiz)
```

<!-- TODO: show screenshot or gif? -->

<br>

## Integrating into your Shiny application

You can integrate the quiz into your Shiny app by adding it to the server and UI functions. Here's an example:

```{r eval=FALSE}
# UI
ui <- fluidPage(
  h3('My Excellent Shiny App'),
  quiz_ui(quiz)
)

# Server
server <- function(input, output) {
  quiz_server(quiz)
}

shinyApp(ui = ui, server = server)
```

## Adjusting options

There are several options you can adjust to customize the behavior of your quizzes. Here are some examples:

- `ns`: A namespace function created from `shiny::NS()`. The default is `shiny::NS('quiz')`. When including multiple quizzes within an application or when nesting a quiz within a module, this should adjusted in addition to the `ns` argument within each `create_question()`.  
- `messages`: A `messages` object created from `create_messages()`. Controls the messages shown at the end of the quiz. 
- `sandbox`: Should the quiz be put into sandbox mode? TRUE/FALSE. Sandbox resamples the questions so they go on quasi-infinitely.  
- `end_on_first_wrong`: Should the quiz terminate once the user gets one question wrong? Defaults to TRUE.  
- `progress_bar`: Show the progress bar? Defaults to TRUE.    
- `progress_bar_color`: Color of the progress bar. Can be a hex code or rgba(). Default is #609963.     

```{r eval=FALSE}
create_quiz(q1, q2, q3, q4, options = set_quiz_options(sandbox = TRUE))
```

<br>

## Consuming the quiz output

The `quiz_server()` outputs a reactive summary of the quiz that can be consumed by your Shiny application. Here, we print it using `verbatimTextOutput` and `renderPrint`. You can pass the summary to any other functions as you wish.

```{r eval=FALSE}
# UI
ui <- fluidPage(
  h3('My Excellent Shiny App'),
  quiz_ui(quiz),
  verbatimTextOutput('quizSummary')
)

# Server
server <- function(input, output) {
  quiz_summary <- quiz_server(quiz)
  output$quizSummary <- shiny::renderPrint(quiz_summary())
}

shinyApp(ui = ui, server = server)
```


That's the basic idea! With the `shinyQuiz` package, you can easily create interactive quizzes and add them to your Shiny applications. Enjoy quiz making! 
