---
title: "Creating Randomized Questions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating Randomized Questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r warning=FALSE, message=FALSE, include=FALSE}
pkgload::load_all()
```

```{r setup}
library(shinyQuiz)
```

Creating a dynamic quiz can make it more engaging and challenging for users. The `create_question_random()` function in `shinyQuiz` allows you to generate random questions. This vignette will guide you through how to use this function effectively.

The `create_question_random()` function takes two main arguments:  
- .f: A function that generates a single random question.  
- n: The number of random questions to generate for the quiz.

<br>

## Creating a Random Question Generator
Before you can use `create_question_random()`, you'll need to create a function that generates a single random question. This function should return a question object created by `create_question()` or `create_question_raw()`.

Here's an example that generates a random question about whether a number is even or odd:

``` {r eval=FALSE}
random_question <- function() {
  number <- round(rnorm(1, 30, 10), 0)
  rand_prompt <- paste('Is', number, 'an even number?')

  q <- create_question(
    prompt = rand_prompt,
    add_choice('Yes, it is even', correct = number %% 2 == 0),
    add_choice('No, it is odd', correct = number %% 2 != 0)
  )

  return(q)
}
```

You can test your function by running it a few times and verifying the preview changes each time.

``` {r eval=FALSE}
random_question()
random_question()
```

## Putting It All Together
Once you have your random question generator function, you can pass it to `create_question_random()` along with the number of questions you want to generate.

``` {r eval=FALSE}
create_quiz(
  create_question_random(.f = random_question, n = 20)
)
```

This will create a quiz with 20 randomly generated questions about whether numbers are even or odd.

<br>

## Randomizing on-the-fly

Coming soon!

### Pre-Created vs. Dynamic Quizzes
When you run `create_question_random()` outside of a Shiny server function, the set of questions it generates is fixed at that moment. This means that if you deploy a Shiny application with this pre-created quiz, every user will see the same set of questions.

``` {r eval=FALSE}
# Pre-created quiz
my_quiz <- create_quiz(
  create_question_random(.f = random_question, n = 20)
)
```

### Dynamic Randomization within Shiny Server
To generate a new set of questions for each user or session, you can include `create_question_random()` within your Shiny app's server function. This way, the function will re-execute each time a new user accesses the app, providing a unique set of questions.

``` {r eval=FALSE}
# create static quiz for the ui side
# this is required for namespace
quiz <- create_quiz(
  create_question_random(.f = random_question, n = 20)
)

# build the shiny UI
ui <- shiny::fluidPage(
  htmltools::div(
    style = "max-width: 700px",
    quiz_ui(quiz)
  )
)

# build the server
server <- function(input, output, session) {
  # create the dynamic quiz
  quiz <- create_quiz(
    create_question_random(.f = random_question, n = 20)
  )
  
  # run the quiz server
  quiz_server(quiz)
}

# run the app
shiny::shinyApp(ui, server)
```

By placing create_question_random() inside the server function, you ensure that the quiz is dynamic, offering a different experience for each user or at different times.

<br>

## Additional Information

Note that the presence of a sandbox question in a quiz will automatically set the quiz option of `sandbox = TRUE`. This removes the progress bar along the top and changes the behavior...

You may mix and match sandbox and regular questions. The following will create a quiz that starts with one static question and then follows with 20 random ones.

``` {r eval=FALSE}
create_quiz(
  create_question(
    prompt = 'My prompt explaining what the ATC of this thing should be',
    add_slider(0, 30, 15, correct = 10)
  ),
  create_question_random(.f = random_question, n = 20)
)
```

<br>

That's it! Be sure to check out the documentation for `create_question_random()` for more information.